Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-07 paper/manuscript/appendix.Rmd
reorder appendix, integrate several google doc changes

---
title: Appendix to 'Detecting social information in a dense database of infants’ natural
  visual experience'
date: "`r Sys.Date()`"
output:
  papaja::apa6_pdf: default
---

```{r, echo=F, message=F}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
library(stargazer)
library(magick)
library(ggeffects)

theme_set(theme_classic())

knitr::opts_chunk$set(echo=F, warning=F, cache=T, 
                      message=F, sanitize = T)
```

@@

```{r}
## Load in gold sample detections
load(here::here('data/preprocessed_data_2022/gold_sample_annotations2020-01-31.RData')) # human annotations
load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_with_centerall_detections.RData'))

# all_gold_sample_frames_op_hc = load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_high_conf_detections.RData')) 
```

@@

```{r}
## Move to appendix
## get out summary by age for goldset hand-labeled frames
vid_info <- all_vid_data  %>%
  select(child_id, vid_name, age_days, age_day_bin)

@@

# Face/hand detections relative to human annotations
```{r goldSetSanity, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset. Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. Dashed lines show estimated trend lines from proportion of faces/hands in view when analyzing the gold set of frames made by human annotators. Dotted lines show trend lines from the goldset when frames containing children's own hands were excluded." }

@@

# Density of child vs. adults hands in the visual field

```{r} 
### Load turk hand annotations with all bounding boxes (multiple dets per frame)
load(here::here('data/preprocessed_data_2022/hand_annotations_2020-01-29.RData'))

@@

# Distribution of faces and hands in the visual field
We explored where in the visual field children tended to see faces and hands, suspecting that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank (2012). 
As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located (see Figure).
However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ visual environment from 6 months of age.

```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 5-31 months of age. Each dot represents the average position from one video within a given age range.", warning=F}

# Detection threshold estimations

@@

```{r roc_curves, fig.width=6.5, fig.height=3.2, fig.cap="ROC curves relating the rate of true vs. false positives for both face and hand detections at each level of detector confidence thresholds (lighter values = stricter cutoffs)."}
ggarrange(face_roc, hand_roc, nrow=1)
```

# OpenPose Error Analyses
```{r}
# remove big data frame with thresholds
rm(all_gold_sample_frames_op)

@@

```{r det_perf_by_age, fig.width=6.5, fig.height=3.1, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}

@@

ggarrange(p1, p2, nrow=1)
```

@@

ggarrange(p1, p2, nrow=1)
```

# OpenPose Annotation Examples
```{r include=FALSE}
# load(file = here::here('data/preprocessed_data_2022/goldset_category_annotations.RData'))

@@

## Location of OpenPose False Positives

Below we visualize the locations of the 1229 faces (in 1093 frames) that OpenPose detected in the gold set frames that were not actually there, as well as the 1778 OpenPose false positive hands (in 1237 frames) from the gold set.
The average location of OpenPose's false positives for both faces (left) and hands (right) are somewhat more common in the center of the frame, but some are scattered across the frame.
Qualitatively, the location of these false positives do not look much different than the true positive detections.

# Activity by Location

```{r activities_by_lo, fig.width=6.5, fig.height=3.2, fig.cap="Counts of activities by location, including multilocation videos."}
meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

# multi-location videos
meta_long %>% filter(Activity!="N/A", Activity!="Consequence", Activity!="Kicking",
                     Activity!="Gesturing", Activity!="Look and Listen", 
                     Location!="N/A", Location!="California Room",
                     Location!="Rapidly Moving Between Locations", Location!="Piano Room") %>%
  mutate(Location = ifelse(Location=="Dog Park/Park/Field", "Off Property", Location)) %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Activity, y=Location, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Motor Milestones Analysis Details

@@

## Sitting

@@

## Cruising

@@

## Walking

@@

>>>>

```{r, echo=F, message=F}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
library(stargazer)
library(magick)
library(ggeffects)
library(papaja)
theme_set(theme_few())
knitr::opts_chunk$set(echo=F, warning=F, cache=T, 
                      message=F, sanitize = T)
```

@@

```{r}
## Load in gold sample detections
load(here::here('data/preprocessed_data_2022/gold_sample_annotations2020-01-31.RData')) # human annotations
load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_with_centerall_detections.RData')) 
```

@@

```{r}
## get out summary by age for goldset hand-labeled frames
vid_info <- all_vid_data  %>%
  select(child_id, vid_name, age_days, age_day_bin)

@@

## A1 OpenPose Annotation Examples
```{r include=FALSE}
# load(file = here::here('data/preprocessed_data_2022/goldset_category_annotations.RData'))

@@

## A2 Density of child vs. adults hands in the visual field
```{r} 
### Load turk hand annotations with all bounding boxes (multiple dets per frame)
load(here::here('data/preprocessed_data_2022/hand_annotations_2020-01-29.RData'))

@@

## A3 Location of OpenPose False Positives
Below we visualize the locations of the 1229 faces (in 1093 frames) that OpenPose detected in the gold set frames that were not actually there, as well as the 1778 OpenPose false positive hands (in 1237 frames) from the gold set.
The average location of OpenPose's false positives for both faces (left) and hands (right) are somewhat more common in the center of the frame, but some are scattered across the frame.
Qualitatively, the location of these false positives do not look much different than the true positive detections.

## A4 Detection threshold estimations

@@

```{r roc_curves, fig.width=6.5, fig.height=3.2, fig.env="figure", fig.cap="ROC curves relating the rate of true vs. false positives for both face and hand detections at each level of detector confidence thresholds (lighter values = stricter cutoffs)."}
ggpubr::ggarrange(face_roc, hand_roc, nrow=1)
```

## A5/A6 OpenPose Error Analyses
```{r}
# remove big data frame with thresholds
rm(all_gold_sample_frames_op)

@@

```{r det_perf_by_age, fig.width=6.5, fig.env="figure", fig.height=3.1, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}

@@

ggpubr::ggarrange(p1, p2, nrow=1)
```

@@

ggpubr::ggarrange(p1, p2, nrow=1)
```

## A7 Face/hand detections relative to human annotations
```{r goldSetSanity, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset. Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. Dashed lines show estimated trend lines from proportion of faces/hands in view when analyzing the gold set of frames made by human annotators. Dotted lines show trend lines from the goldset when frames containing children's own hands were excluded." }

@@

## Tables 1&2 Motor Milestones Analysis Details

@@

### Sitting

@@

### Cruising

@@

### Walking

@@

## A8 Activity by Location

```{r}
meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

```{r activities_by_lo, fig.width=6.5, fig.height=3.2, fig.cap="Counts of activities by location, including multilocation videos."}

# multi-location videos
meta_long %>% filter(Activity!="N/A", Activity!="Consequence", Activity!="Kicking",
                     Activity!="Gesturing", Activity!="Look and Listen", 
                     Location!="N/A", Location!="California Room",
                     Location!="Rapidly Moving Between Locations", Location!="Piano Room") %>%
  mutate(Location = ifelse(Location=="Dog Park/Park/Field", "Off Property", Location)) %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Activity, y=Location, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

## A9 Distribution of faces and hands in the visual field
We explored where in the visual field children tended to see faces and hands, suspecting that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank (2012). 
As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located (see Figure).
However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ visual environment from 6 months of age.

```{r faceHandDensity, fig.env="figure", fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 5-31 months of age. Each dot represents the average position from one video within a given age range.", warning=F}
